Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data

### 2021-08-06 Manuscript/02-Method.Rmd
Run pipeline

\matrix (linearPrior) [matrix of nodes, column sep = 0mm, row sep = 0.7cm] {
&\node (linearTheta) [outCome] { $\theta_j^{0}\sim Beta(a, b)$ };\\
&\node (linearGamma) [outCome] { $\gamma_j^0 \sim Bin(1, \theta_j^0) $ };\\
&\node (linearBeta) [outCome] { $\beta_j^0 \sim DE(0,(1-\gamma^0_{j}) s_0 + \gamma^0_{j} s_1)$};\\
};

\matrix (penPrior) [right = 2cm of linearPrior, matrix of nodes, column sep = 0mm, row sep = 0.7cm] {
\node (penTheta) [outCome] { $\theta_{j}^\tp\sim Beta(a, b)$ };\\
\node (penGamma) [outCome] { $\gamma_{j}^\tp \sim Bin(1, \theta_j^\tp)$ };\\
\node (penBeta) [outCome] { $\beta_{jk}^\tp \sim  DE(0,(1-\gamma^0_{j}) s_0 + \gamma^0_{j} s_1)$};\\
};

\node (ab)[staticCompo] at ($(linearTheta)!0.5!(penTheta)$) {$(a, b)$};
%\node (PenaltyPrior) [PriorBoarder,  right = 1cm of ab] {part 2};
\node (s) [staticCompo]  at ($(linearBeta)!0.5!(penBeta)$)  {($s_0, s_1$)};

\node (Beta) [staticCompo, below = 1cm of s] {$\bs \beta = (\beta^0_1, \bs \beta^\tp_1, \dots,\beta^0_j, \bs \beta^\tp_j , \dots,\beta^0_p, \bs \beta^\tp_p) $};
\node (Y) [outCome, below = 1cm of Beta] {$y_i \sim Expo. Fam. (g(\eta_i))$};

%Lines

\draw[->] (linearTheta) -- (linearGamma);
\draw[->] (penTheta) -- (penGamma);
\draw[->] (linearGamma) -- (linearBeta) ;
\draw[->] (penGamma) -- (penBeta);
\draw[->] (ab) -- (linearTheta);
\draw[->] (ab) -- (penTheta);
\draw[->] (s) -- (linearBeta) ;
\draw[->] (s) -- (penBeta);
\draw[->] (linearBeta) -- (Beta);
\draw[->] (penBeta) -- (Beta);
\draw[->] (Beta) --  (Y);

% Now that the diagram has been drawn, background rectangles
% can be fitted to its elements. This requires the TikZ
% libraries "fit" and "background".
% Control input and measurement are labeled. These labels have
% not been translated to English as "Measurement" instead of
% "Messung" would not look good due to it being too long a word.
\begin{pgfonlayer}{background}
    \node [background,
                fit=(linearTheta) (linearBeta),
                label=above:Null Space:] {};
    \node [background,
                 fit=(penTheta) (penBeta),
                label=above:Penalized Space:] {};

\end{pgfonlayer}
\end{tikzpicture}

>>>>

\matrix (linearPrior) [matrix of nodes, column sep = 0mm, row sep = 0.7cm] {
  \node (linearGamma) [outCome] { $\gamma_j^0 \sim Bin(1, \theta_j^0) $ };\\
  \node (linearBeta) [outCome] { $\beta_j^0 \sim DE(0,(1-\gamma^0_{j}) s_0 + \gamma^0_{j} s_1)$};\\
};
\matrix (penPrior) [right = 2cm of linearPrior, matrix of nodes, column sep = 0mm, row sep = 0.7cm] {
  \node (penGamma) [outCome] { $\gamma_{j}^\tp \sim Bin(1, \theta_j^\tp)$ };\\
  \node (penBeta) [outCome] { $\beta_{jk}^\tp \sim  DE(0,(1-\gamma^0_{j}) s_0 + \gamma^0_{j} s_1)$};\\
};

\node (s) [staticCompo]  at ($(linearBeta)!0.5!(penBeta)$)  {($s_0, s_1$)};
\node (Beta) [staticCompo, below = 1cm of s] {$\bs \beta = (\beta^0_1, \bs \beta^\tp_1, \dots,\beta^0_j, \bs \beta^\tp_j , \dots,\beta^0_p, \bs \beta^\tp_p) $};
\node (Theta)[outCome, above = 2cm of s] {$\theta_{j} \sim Beta(a, b)$};
\node (ab)[staticCompo, above = 0.5cm of Theta] {$(a, b)$};
\node (Y) [outCome, below = 1cm of Beta] {$y_i \sim Expo. Fam. (g(\eta_i))$};

\draw[->] (Theta) -- (linearGamma);
\draw[->] (Theta) -- (penGamma);
\draw[->] (linearGamma) -- (linearBeta) ;
\draw[->] (penGamma) -- (penBeta);
\draw[->] (ab) -- (Theta);
\draw[->] (s) -- (linearBeta) ;
\draw[->] (s) -- (penBeta);
\draw[->] (linearBeta) -- (Beta);
\draw[->] (penBeta) -- (Beta);
\draw[->] (Beta) --  (Y);

\begin{pgfonlayer}{background}
  \node [background,
   fit=(linearGamma) (linearBeta),
   label=above:Null Space:] {};
  \node [background,
    fit=(penGamma) (penBeta),
    label=above:Penalized Space:] {};
\end{pgfonlayer}

\end{tikzpicture}

### 2021-08-06 Manuscript/SS_GAM.tex
Run pipeline

\matrix (linearPrior) [matrix of nodes, column sep = 0mm, row sep = 0.7cm] {
&\node (linearTheta) [outCome] { $\theta_j^{0}\sim Beta(a, b)$ };\\
&\node (linearGamma) [outCome] { $\gamma_j^0 \sim Bin(1, \theta_j^0) $ };\\
&\node (linearBeta) [outCome] { $\beta_j^0 \sim DE(0,(1-\gamma^0_{j}) s_0 + \gamma^0_{j} s_1)$};\\
};

\matrix (penPrior) [right = 2cm of linearPrior, matrix of nodes, column sep = 0mm, row sep = 0.7cm] {
\node (penTheta) [outCome] { $\theta_{j}^\text{pen}\sim Beta(a, b)$ };\\
\node (penGamma) [outCome] { $\gamma_{j}^\text{pen}\sim Bin(1, \theta_j^\text{pen})$ };\\
\node (penBeta) [outCome] { $\beta_{jk}^\text{pen}\sim  DE(0,(1-\gamma^0_{j}) s_0 + \gamma^0_{j} s_1)$};\\
};

\node (ab)[staticCompo] at ($(linearTheta)!0.5!(penTheta)$) {$(a, b)$};
%\node (PenaltyPrior) [PriorBoarder,  right = 1cm of ab] {part 2};
\node (s) [staticCompo]  at ($(linearBeta)!0.5!(penBeta)$)  {($s_0, s_1$)};

\node (Beta) [staticCompo, below = 1cm of s] {$\boldsymbol{\beta }= (\beta^0_1, \boldsymbol{\beta}^\text{pen}_1, \dots,\beta^0_j, \boldsymbol{\beta}^\text{pen}_j , \dots,\beta^0_p, \boldsymbol{\beta}^\text{pen}_p) $};
\node (Y) [outCome, below = 1cm of Beta] {$y_i \sim Expo. Fam. (g(\eta_i))$};

%Lines

\draw[->] (linearTheta) -- (linearGamma);
\draw[->] (penTheta) -- (penGamma);
\draw[->] (linearGamma) -- (linearBeta) ;
\draw[->] (penGamma) -- (penBeta);
\draw[->] (ab) -- (linearTheta);
\draw[->] (ab) -- (penTheta);
\draw[->] (s) -- (linearBeta) ;
\draw[->] (s) -- (penBeta);
\draw[->] (linearBeta) -- (Beta);
\draw[->] (penBeta) -- (Beta);
\draw[->] (Beta) --  (Y);

% Now that the diagram has been drawn, background rectangles
% can be fitted to its elements. This requires the TikZ
% libraries "fit" and "background".
% Control input and measurement are labeled. These labels have
% not been translated to English as "Measurement" instead of
% "Messung" would not look good due to it being too long a word.
\begin{pgfonlayer}{background}
    \node [background,
                fit=(linearTheta) (linearBeta),
                label=above:Null Space:] {};
    \node [background,
                 fit=(penTheta) (penBeta),
                label=above:Penalized Space:] {};

\end{pgfonlayer}
\end{tikzpicture}

>>>>

\matrix (linearPrior) [matrix of nodes, column sep = 0mm, row sep = 0.7cm] {
  \node (linearGamma) [outCome] { $\gamma_j^0 \sim Bin(1, \theta_j^0) $ };\\
  \node (linearBeta) [outCome] { $\beta_j^0 \sim DE(0,(1-\gamma^0_{j}) s_0 + \gamma^0_{j} s_1)$};\\
};
\matrix (penPrior) [right = 2cm of linearPrior, matrix of nodes, column sep = 0mm, row sep = 0.7cm] {
  \node (penGamma) [outCome] { $\gamma_{j}^\text{pen}\sim Bin(1, \theta_j^\text{pen})$ };\\
  \node (penBeta) [outCome] { $\beta_{jk}^\text{pen}\sim  DE(0,(1-\gamma^0_{j}) s_0 + \gamma^0_{j} s_1)$};\\
};

\node (s) [staticCompo]  at ($(linearBeta)!0.5!(penBeta)$)  {($s_0, s_1$)};
\node (Beta) [staticCompo, below = 1cm of s] {$\boldsymbol{\beta }= (\beta^0_1, \boldsymbol{\beta}^\text{pen}_1, \dots,\beta^0_j, \boldsymbol{\beta}^\text{pen}_j , \dots,\beta^0_p, \boldsymbol{\beta}^\text{pen}_p) $};
\node (Theta)[outCome, above = 2cm of s] {$\theta_{j} \sim Beta(a, b)$};
\node (ab)[staticCompo, above = 0.5cm of Theta] {$(a, b)$};
\node (Y) [outCome, below = 1cm of Beta] {$y_i \sim Expo. Fam. (g(\eta_i))$};

\draw[->] (Theta) -- (linearGamma);
\draw[->] (Theta) -- (penGamma);
\draw[->] (linearGamma) -- (linearBeta) ;
\draw[->] (penGamma) -- (penBeta);
\draw[->] (ab) -- (Theta);
\draw[->] (s) -- (linearBeta) ;
\draw[->] (s) -- (penBeta);
\draw[->] (linearBeta) -- (Beta);
\draw[->] (penBeta) -- (Beta);
\draw[->] (Beta) --  (Y);

\begin{pgfonlayer}{background}
  \node [background,
   fit=(linearGamma) (linearBeta),
   label=above:Null Space:] {};
  \node [background,
    fit=(penGamma) (penBeta),
    label=above:Penalized Space:] {};
\end{pgfonlayer}

\end{tikzpicture}
